---
# Clinic parameter options are: 
# All, AF Williams, Boulder, Lone Tree, Westminster, WISH
# Options do not need to be in quotes
params:
  clinic: "WISH"
    
title: "DFM Health Equities Survey 2024"
subtitle: "`r params$clinic`"
date: "`r format(Sys.time(), '%B %d %Y')`"

# Quarto docx settings ---------------------------------------------------------
# fig height, width, and dpi set to prevent overplotting and image quality
format:
  docx:
    toc: true
    reference-doc: "../qmd_reference/custom-reference-doc.docx"
    output-file: report.docx
  
editor: source
  
execute: 
  echo: false
  warning: false
---

```{r load libraries}
library(magrittr, include.only = "%<>%")

pacman::p_load(tidyverse,
               gtsummary,
               REDCapR,
               GGally,
               docstring,
               install = FALSE)
```

```{r pull_data()}
pull_report <- function(report_id, val_type, header_type) {

  #' pull_report
  #'
  #' Pulls a pre-specified report from RedCap given a REDCap report ID,
  #' the value type, and the header type.
  #'
  #' @param report_id the redcap report id
  #' @param val_type responses as 'raw' for numbers or 'label' for character
  #' @param header_type 'raw' for the redcap field name, 'label' for the text

  # Credentials files set as an environmental variable. Placed in a central
  # directory to prevent accidentally uploading tokens to GitHub
  path_credential <- Sys.getenv("redcap_credentials")

  # Project 28323 corresponds to REDCap Health Equity Survey II
  project_id <- 28323

  .token <- retrieve_credential_local(
    path_credential,
    project_id,
    check_url = TRUE,
    check_username = FALSE,
    check_token_pattern = TRUE,
    username = NA_character_
  )$token

  url <- "https://redcap.ucdenver.edu/api/"

  formData <- list("token" = .token,
                   content = 'report',
                   format = 'csv',
                   report_id = report_id,
                   csvDelimiter = '',
                   rawOrLabel = val_type,
                   rawOrLabelHeaders = header_type,
                   exportCheckboxLabel = 'true',
                   returnFormat = 'json'
                   )

  response <- httr::POST(url, body = formData, encode = "form")

  data <- httr::content(response)

  # Remove the <br> and white space from likert columns only if the responses
  # are in label format (character)
  data <- data %>%
    mutate_if(is.character, ~ str_replace(., "<br>", replacement = '')) %>%
    mutate_if(is.character, ~ str_trim(.))

  return(data)
}
```

```{r, pull data}
# Pull the 2024 report in label format w/ out the demographic race columns and 
# clinic name
data_lab <- pull_report('128507', 'label', 'raw') %>%
  select(-(contains("demographic_4_race")), -(contains("clinic_name")))

# Pull the 2024 report in raw format for the demographic race anc clinic_name
# columns only
data_raw <- pull_report('128507', 'raw', 'raw') %>%
  select(contains("demographic_4_race"), -(contains("clinic_name")))

# Merge the race cols into the main data frame
data <- bind_cols(data_lab, data_raw)

# Drop record id 171 because it was a test record
data %<>%
  filter(record_id != 171)

# Remove the race data frame
rm(data_raw, data_lab)


# Pull the column headers in label format for displaying in tables/charts
col_labs <- names(
  (pull_report('128507', 'raw', 'label') %>% select(-(contains("Clinic Name"))))
  )
```

```{r}
# Modify the column names by removing the _2024 and _v1 suffixes
new_col_names <-
  colnames(data) %>%
  str_replace(., '_2024', replacement = '') %>%
  str_replace(., '_v1', replacement = '')

# Set the new column names to harmonize column names in R
colnames(data) <- new_col_names

# Create a data frame with the column names and their corresponding column
# labels
labels <- data.frame(t(col_labs))
colnames(labels) <- new_col_names
```

```{r}
# Set columns to factor and order the levels
# Q1:
data %<>%
  mutate(across(hi_problems_q1:hi_problems_q3,
                ~ factor(., levels = c("Not a problem at all",
                                       "Minor problem",
                                       "Moderate problem",
                                       "Serious problem"))))

# Q2
data %<>%
  mutate(across(hi_clinic_q1:hi_clinic_implicit,
                ~ factor(., levels = c("Not at all",
                                       "Slightly",
                                       "Moderately",
                                       "Very much",
                                       "Extremely"))))

# Collapse very much and extremely
data %<>%
  mutate(across(hi_clinic_q1:hi_clinic_implicit,
                ~ fct_collapse(., `Very much/Extremely` = c("Very much", "Extremely"))))

  
# Q3.1, Q4
data %<>%
  mutate(across(c(hi_individual_q1, hi_clinicleaders_q1),
                ~ factor(., levels = c("Not important at all",
                                       "Slightly important",
                                       "Moderately important",
                                       "Extremely important"))))


# Q5,Q14
data %<>%
  mutate(across(c(meaningful_change, org_awareness, org_collab),
                ~ factor(., levels = c("Strongly disagree",
                                       "Disagree",
                                       "Agree",
                                       "Strongly agree"))))

# Q6
data %<>%
  mutate(across(clinic_hefocus,
                ~ factor(., levels = c("Far too little",
                                       "Too little",
                                       "The right amount",
                                       "Too much",
                                       "Far too much"))))

# Q8
data %<>%
  mutate(across(dash_aware,
                ~ factor(.,
                         levels = c("I did not know they existed.",
                                    "I knew they existed but have never seen the data.",
                                    "I knew they existed and have seen the data.",
                                    "I knew they existed, have seen the data, and have used at least some of the data to shape local operations or clinical work."))))

# Q10
data %<>%
  mutate(across(sw_skills:sw_clinicianavail,
                ~ factor(., levels = c('Strength',
                                       'Unsure',
                                       'Challenge'))))

# Q12
data %<>%
  mutate(across(confidence_disability,
                ~ factor(., levels = c('Not at all confident',
                                       'Not very confident',
                                       'Somewhat confident',
                                       'Very confident'))))

# Q13
data %<>%
  mutate(across(disability_time:disability_other,
                ~ factor(., levels = c('Not at all a barrier',
                                       'Small barrier',
                                       'Moderate barrier',
                                       'Large barrier'))))
```


<!-- If clinic is set to all, then display the response rate. Cannot display a 
response rate per clinic, since those that did not respond would not have a 
clinic value to filter. -->

`r if(params$clinic == "All"){'# Response Rate'}`
```{r}
if(params$clinic == "All") {
  show_response_rate <-  TRUE
} else {
  show_response_rate <- FALSE
}
```

```{r, eval=show_response_rate}
data %>%
  select(health_equity_in_dfm_practices_survey_complete) %>%
  tbl_summary(label = list(health_equity_in_dfm_practices_survey_complete = "Survey Complete")) %>%
  as_gt()
```

```{r}
# Filter data to complete responses only
data %<>%
  filter(health_equity_in_dfm_practices_survey_complete == "Complete")
```

```{r}
# filter data to clinic level
if (params$clinic != 'All') {
  data %<>%
    filter(demographic_1_practice == params$clinic)
}
```

# Participant Characteristics
```{r}
data <- data %>%
    rename(Practice = demographic_1_practice,
           Role = demographic_2_role,
           Age = demographic_3_age,
           Gender = demographic_6_gender,
           Transgender = demographic_8_transgender,
           Disability = demographic_9_disability,
           Residency = demographic_residency)

# Factor and set levels for demographic questions
# Modify Gender, Transgender, and Disability
data <- data %>%
  mutate(Gender = factor(Gender,
                           levels = c("Woman", "Man",
                                      "Nonbinary/Gender Non-Conforming",
                                      "Other (please specify)",
                                      "Prefer not to answer")),
         Transgender = factor(Transgender,
                                levels = c("Yes", "No",
                                           "Prefer not to answer")),
         Disability = factor(Disability,
                               levels = c("Yes", "No",
                                          "Prefer not to answer")))

# Modify Role values to shorten the display of "Clinician/Provider"
data %<>%
  mutate(Role = ifelse(Role == "Clinician/Provider (medical, behavioral health, pharmacy)", 
                       "Clinician/Provider", Role))

# Set anyone who did not respond to Role as unknown, otherwise they don't get
# counted
if (sum(is.na(data$Role)) != 0) {
  data %<>%
    mutate(Role = fct_na_value_to_level(Role, level = "Unknown Role"))
}


# Modify time at clinic for displaying in tables and set the levels
data %<>%
  mutate(`Time at clinic` = factor(time_at_clinic,
                                 levels = c('less than 1 year',
                                            '1-5 years',
                                            'longer than 5 years')))

if (sum(is.na(data$`Time at clinic`)) != 0) {
  data %<>%
    mutate(`Time at clinic` = fct_na_value_to_level(`Time at clinic`, 
                                                    level = "Unknown"))
}

# Set a vector of the race & ethnicity variables to facilitate selecting columns
# Use the un factored columns because they are coded as 0 or 1 instead of
# Checked/Unchecked. Do not include 'other' because it contains free text.
race_vars <- names(data %>%
                     select(starts_with("demographic") &
                              contains("race") &
                              !contains(".factor") &
                              !contains("other")))

# Set the race variables to factor to display in demographic table
data <- data %>%
  mutate(across(race_vars, ~ factor(., levels = c("0", "1"))))

# Convert NAs to explicit values for tabulation
data %<>%
  mutate(across(c(Age, Gender, Disability),
                ~ fct_na_value_to_level(., level = "Unknown")))
```

```{r}
data %>%
  select(Role,
         `Time at clinic`,
         Age,
         Gender,
         Transgender,
         Disability,
         all_of(race_vars)) %>%
  tbl_summary(by = "Role",
              label = list(
                demographic_4_race___1 = "American Indian / Alaska Native",
                demographic_4_race___2 = "Asian",
                demographic_4_race___3 = "Black or African American",
                demographic_4_race___4 = "White",
                demographic_4_race___5 = "Hispanic or Latino",
                demographic_4_race___6 = "Another race",
                demographic_4_race___8 = "Prefer not to answer"),
              value = list(demographic_4_race___1 ~ "1",
                           demographic_4_race___2 ~ "1",
                           demographic_4_race___3 ~ "1",
                           demographic_4_race___4 ~ "1",
                           demographic_4_race___5 ~ "1",
                           demographic_4_race___6 ~ "1",
                           demographic_4_race___8 ~ "1")) %>%
  add_overall() %>%
  modify_header(label = "Participant Characteristics") %>%
  bstfun::add_variable_grouping("Race/Ethnicity" = race_vars) %>%
  bold_labels() %>% # Bold labels will make all race/ethnicity variable bold
  modify_table_styling(columns = label,
                       rows = variable == "demographic_4_race___1",
                       undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___2",
                     undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___3",
                     undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___4",
                     undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___5",
                     undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___6",
                     undo_text_format = "bold") %>%
  modify_table_styling(columns = label,
                     rows = variable == "demographic_4_race___8",
                     undo_text_format = "bold") %>%
  as_gt()
```


```{r}
freq_prop_tab <- function(df) {
  #' freq_prop_tab
  #'
  #' Returns a gt_summary() table of columns with categorical responses. This
  #' function was designed to display Likert type responses. It requires the
  #' the labels data frame in the global environment to change the display of
  #' column headers as labels instead of the redcap fields
  #'
  #' @param df a dataframe that has only the columns of interest to tabulate
  
  role <- df %>% select(Role)
  
  df <- df %>% select(-Role)
  
  vars <- names(df)

  var_labs <- labels %>% select(all_of(vars)) %>% as.character()

  # Draft code of trying to set unknown to columns that have missing only
  # set_unknown <- function(var) {
  #   
  #   n_missing <- df %>%
  #     select(var) %>%
  #     filter(var) %>%
  #     nrow()
  #   
  #   if (n_missing > 0) {
  #     df %<>% 
  #       mutate(var = fct_na_value_to_level(var, level = "Unknown"))
  #     
  #   }
  # }
  # 
  # df %>%
  #   mutate(across(everything(), ~ set_unknown(!!sym(.))))
  df <- df %>%
    mutate(across(everything(), ~ fct_na_value_to_level(., level = "Unknown"))) %>%
    rename_at(all_of(vars), ~ var_labs)
    
  tab <- bind_cols(role, df) %>%
    tbl_summary(by = Role) %>%
    bold_labels() %>%
    modify_header(label = "") %>% 
    add_overall() %>%
    as_gt()

  return(tab)
}
```

# Q1: In your opinion, how much of a problem are health inequities
```{r}
data %>%
  select(Role, hi_problems_q1:hi_problems_q3) %>%
  freq_prop_tab(.)
```

```{r}
q1_plot <- function(var, label) {
  #' generate q1_plot
  #'
  #' Creates a flipped, clustered bar chart for the hi_problems_q1 through 
  #' hi_problems_q3 sub questions in Q1. References the "data" data frame from
  #' the global environment
  #'
  #' @param var a quoted string for selecting the column to be plotted 
  #'  hi_problems_q1, hi_problems_q3, or hi_problems_q3
  #' @param label a quoted string to use as the plot title
  
  
  # Create a data frame for calculating the frequencies and proportions for all
  # available responses. Role is renamed as Overall so that the data can be
  # stacked in long format with the role data frame to plot both the overall and
  # role specific responses in one figure.
  overall <-
    data %>% 
    select(Role, sym(var)) %>% 
    mutate(Role = 'Overall') %>%
    group_by(Role, !!sym(var)) %>%
    summarise(Frequency = n(), .groups = "drop") %>%
    mutate(Proportion = Frequency/nrow(data))

  # Create a data frame with the frequencies of participants by Role, these will
  # be used as the Role specific denominators
  n_group <- data %>%
    select(Role, sym(var)) %>%
    group_by(Role) %>%
    summarise(n_group = n())

  # Create a data set of frequencies after grouping by role and response.
  role <- 
    data %>% 
    select(Role, sym(var)) %>%
    group_by(Role, !!sym(var)) %>%
    summarise(Frequency = n(), .groups = "drop")
  
  # Merge role and and n_group to calculate frequencies and proportions broken
  # out by role. Then remove n_group so that it can be stacked with the overall
  # data frame that contains the overall responses. n.b. does not plot those
  # that either had an Unknown Role or an Unknown response
  left_join(role, n_group, by = "Role") %>%
    mutate(Proportion = Frequency/n_group) %>%
    select(-n_group) %>%
    bind_rows(., overall) %>%
    filter(sym(var) != "Unknown",
           Role != "Unknown Role") %>%
    drop_na(sym(var)) %>%
    mutate(Role = factor(Role, levels = c("Unknown Role", 
                                          "Staff", "Clinician/Provider", 
                                          "Overall"))) %>%
    ggplot(aes(x = !!sym(var), y = Proportion, fill = Role)) +
    geom_col(alpha = 0.8, 
             position = position_dodge2(width = 0.9, preserve = "single")) +
    theme_minimal()+
    scale_fill_brewer(type = "qual", palette = 2) +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) +
    labs(y = "Percentage", x = "", title = label) +
    coord_flip() +
    theme(legend.position = "top") +
    guides(fill = guide_legend(title = "", reverse = TRUE))
}
```

```{r, fig.width=6.5, dpi = 600}
q1_plot('hi_problems_q1', label = 'In the United States')
```

```{r, fig.width=6.5, dpi = 600}
q1_plot('hi_problems_q2', label = 'In the UC Health System?')
```

```{r, fig.width=6.5, dpi = 600}
q1_plot('hi_problems_q3', label = 'In your clinic?')
```


# Q2: Among patients at your clinic, how much do you think each of the following contributes to health inequities?
```{r}
data %>%
  select(Role,hi_clinic_q1:hi_clinic_q4, hi_clinic_implicit) %>%
  freq_prop_tab(.)
```


# Q3: How important is it to you to address health inequities within your clinic?
```{r}
data %>%
  select(Role, hi_individual_q1) %>%
  freq_prop_tab()
```

```{r}
# Display table only if there are responses to display
# Westminster 2024 will not have any responses to display
n_responses <- data %>%
  filter(hi_individual_q1 %in% c("Not important at all", 
                                 "Slightly important")) %>%
  nrow()
```

`r if(n_responses != 0){'## Why is it "not important at all" or "slightly important" to address health inequities within your clinic?'}`
```{r}
if(n_responses != 0) {
  show_table <- TRUE
} else {
  show_table <- FALSE
}
```

```{r, eval=show_table}
data %>%
  filter(hi_individual_q1 %in% c("Not important at all", 
                                 "Slightly important")) %>%
  select(Role, hi_individual_q2) %>%
  freq_prop_tab()
```

<!-- If there are responses, then display them . -->
```{r}
n_responses <- data %>%
  select(hi_individual_q3) %>%
  drop_na() %>%
  nrow()
```

`r if(n_responses != 0){'## Other (please specify):'}`
```{r}
if(n_responses != 0) {
  show_table <- TRUE
} else {
  show_table <- FALSE
}
```

```{r, eval=show_table}
# Only one responded to this question, most clinics will not have data for this
# question
data %>%
  select(hi_individual_q3) %>%
  drop_na() %>%
  gt::gt()
```


# Q4: How important is it to your clinic leadership to address health inequities at your clinic?
```{r}
data %>%
  select(Role, hi_clinicleaders_q1) %>%
  freq_prop_tab()
```


# Q5: Please rate how much you agree or disagree with the following statement:
```{r}
data %>%
  select(Role, meaningful_change) %>%
  freq_prop_tab()
```

## Please describe the changes your clinic has made in a few phrases or sentences: Only for those that responded to at least "Agree" above.
```{r}
data %>%
  select(meaningful_change_frsp) %>%
  drop_na() %>%
  gt::gt()
```


# Q6: Do you think your clinic focuses on health equity too little, the right amount, or too much?
```{r}
data %>%
  select(Role, clinic_hefocus) %>%
  freq_prop_tab()
```


# Q7: Have you taken any of the following actions in the last year? (Select all that apply)
```{r}
df <- data %>%
  select(personal_actions_q1___1:personal_actions_q1____66) %>%
    mutate(across(everything(), ~ ifelse(!is.na(.), 1, 0)),
           across(everything(), ~ factor(., levels = c("0", "1"))))

vars <- names(df)

# modify the column header labels for display
var_labs <- labels %>%
  select(all_of(vars)) %>%
  as.character() %>%
  str_remove(".*=") %>%           # removes all characters before '='
  gsub('.{1}$', '', .) %>%        # removes the 1st character from the end ')'
  str_replace("<br>", '') %>%     # removes the '<br>' if available
  str_trim()                      # removes any trailing white space


bind_cols(df, data.frame(Role = data$Role)) %>%
  tbl_summary(by = Role,
              value = list(vars[1] ~ "1",
                           vars[2] ~ "1",
                           vars[3] ~ "1",
                           vars[4] ~ "1",
                           vars[5] ~ "1",
                           vars[6] ~ "1",
                           vars[7] ~ "1"),
              label = list(vars[1] ~ var_labs[1],
                           vars[2] ~ var_labs[2],
                           vars[3] ~ var_labs[3],
                           vars[4] ~ var_labs[4],
                           vars[5] ~ var_labs[5],
                           vars[6] ~ var_labs[6],
                           vars[7] ~ var_labs[7])
              ) %>%
  modify_header(label = "") %>%
  add_overall() %>%
  as_gt()
```

```{r}
# May need to make some data frames and merge in the number of responses per group to come up with %ages
overall <- data %>% 
  select(Role, personal_actions_q1___1:personal_actions_q1____66) %>%
  mutate(Role = 'Overall') %>%
  mutate(across(personal_actions_q1___1:personal_actions_q1____66, ~ ifelse(is.na(.), 0, 1))) %>%
  pivot_longer(cols = personal_actions_q1___1:personal_actions_q1____66,
               names_to = "Question",
               values_to = "Endorsed") %>%
  group_by(Role, Question) %>%
  summarise(Frequency = sum(Endorsed, na.rm = TRUE),
            .groups = 'drop') %>%
  mutate(Proportion = Frequency/nrow(data))


role <- data %>%
  select(Role, personal_actions_q1___1:personal_actions_q1____66) %>%
  mutate(across(personal_actions_q1___1:personal_actions_q1____66, ~ ifelse(is.na(.), 0, 1))) %>%
  pivot_longer(cols = personal_actions_q1___1:personal_actions_q1____66,
               names_to = "Question",
               values_to = "Endorsed") %>%
  group_by(Role, Question) %>%
  summarise(Frequency = sum(Endorsed, na.rm = TRUE),
            n_group = n(),
            .groups = 'drop') %>%
  mutate(Proportion = Frequency/n_group) %>%
  select(-n_group)
```

```{r, fig.width=6.5}
bind_rows(overall, role) %>%
  filter(Role != "Unknown Role") %>%
  mutate(Role = factor(Role, levels = rev(c("Overall", "Clinician/Provider", "Staff")))) %>%
  mutate(Question = fct_collapse(factor(Question),
                               "Health equity training" = "personal_actions_q1___1",
                               "Informal opportunities" = "personal_actions_q1___2",
                               "Changed patient care" = "personal_actions_q1___3",
                               "Changed communication" = "personal_actions_q1___4",
                               "Project participation" = "personal_actions_q1___5",
                               "Leadership feedback" = "personal_actions_q1___6",
                               "Other" = "personal_actions_q1____66")) %>%
  ggplot(aes(x = factor(Question, levels = c(
                               "Other",
                               "Leadership feedback",
                               "Project participation",
                               "Changed communication",
                               "Changed patient care",
                               "Informal opportunities",
                               "Health equity training")), y = Proportion, fill = Role)) +
  geom_col(alpha = 0.8, position = position_dodge2(.9, preserve = 'single')) +
  # geom_text(aes(label = round(Proportion * 100)),
  #           stat = 'identity',
  #           position = position_dodge2(.9, preserve = 'single'),
  #           vjust = 0.4,
  #           hjust = -0.5) +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0,1)) +  
  guides(fill = guide_legend(title = "", reverse = TRUE)) +
  scale_fill_brewer(type = "qual", palette = 2) +
  labs(x = "") +
  theme_minimal() +
  theme(legend.position = "top") +
  coord_flip()
```

```{r, eval = FALSE}
# Chack how many rows of unknown in pa q1_4
data %>%
  filter(Role == 'Unknown Role') %>%
  select(personal_actions_q1___4)
```


# Q8: Your clinic has access to reports that compare healthcare quality data in our patients between different groups (racial/ethnic groups, type of insurance, and whether or not they need an interpreter). This allows our clinics to identify health inequities among their patients.
```{r}
labels <- labels %>%
  mutate(dash_aware = ifelse(dash_aware == 'Your clinic has access to reports that compare healthcare quality data in our patients between different groups (racial/ethnic groups, type of insurance, and whether or not they need an interpreter). This allows our clinics to identify health inequities among their patients. Please describe your experience with these reports.','Please describe your experience with these reports.', dash_aware))

data %>%
  select(Role, dash_aware) %>%
  freq_prop_tab()
```


## We would like to understand how these reports have impacted staff and providers in our family medicine clinics. Please select any statements that you agree with. (Select all that apply) Only for those that responded to at least seeing the data.
```{r}
df <- data %>%
  filter(dash_aware %in% c('I knew they existed and have seen the data.',
                           'I knew they existed, have seen the data, and have used at least some of the data to shape local operations or clinical work.')) %>%
  select(dash_uses___1:dash_uses___5) %>% 
  mutate(across(everything(), ~ ifelse(!is.na(.), 1, 0)))

df_names <- names(df)

index <- df %>%
  colSums() %>%
  order(decreasing = TRUE)

ordered_names <- df_names[index]

df %<>%
  select(all_of(ordered_names)) %>%
  mutate(across(everything(), ~ factor(., levels = c("0", "1"))))


vars <- names(df)

role <- data %>%
  filter(dash_aware %in% c('I knew they existed and have seen the data.',
                           'I knew they existed, have seen the data, and have used at least some of the data to shape local operations or clinical work.')) %>%
  select(Role)

# modify the column header labels for display
var_labs <- labels %>%
  select(all_of(vars)) %>%
  as.character() %>%
  str_remove(".*=") %>%           # removes all characters before '='
  gsub('.{1}$', '', .) %>%        # removes the 1st character from the end ')'
  str_replace("<br>", '') %>%     # removes the '<br>' if available
  str_trim()                      # removes any trailing white space


bind_cols(df, role) %>%
  tbl_summary(by = Role,
              value = list(vars[1] ~ "1",
                           vars[2] ~ "1",
                           vars[3] ~ "1",
                           vars[4] ~ "1",
                           vars[5] ~ "1"),
              label = list(vars[1] ~ var_labs[1],
                           vars[2] ~ var_labs[2],
                           vars[3] ~ var_labs[3],
                           vars[4] ~ var_labs[4],
                           vars[5] ~ var_labs[5])
              ) %>%
  modify_header(label = "") %>%
  add_overall() %>%
  as_gt()
```


# Q9: Every clinic has strengths and challenges when it comes to making changes for health equity.
```{r}
data %>%
  select(Role, sw_skills:sw_clinicianavail) %>%
  freq_prop_tab()
```

```{r, fig.width=6.5, dpi = 600}
q9_plot <- function(sw, title) {
  #' generate q9_plots
  #'
  #' Creates a divergent bar chart for the sw_* select all that apply questions
  #'
  #' @param sw a data frame consisting of all the sw_* questions. Will break if
  #'  not all columns are included. Data can be filtered by Role or other 
  #'  demographic variable
  #' @param title a quoted string to use as the plot title
  
  # A vector of the new column names to display as labels
  new_col_names <- c(
    "KnowledgeSkills",
    "ClinicCulture",
    "UCHCulture",
    "InequityAwareness",
    "Desire",
    "DedicatedTime",
    "Money",
    "Leadership",
    "Relationships",
    "StaffAvailability",
    "ClinicianAvailability")
  
  # Set the new column names
  colnames(sw) <- new_col_names
  
  # Get the index to order the divergent bars by proportion of strength 
  # responses
  index <- sw %>%
    mutate(across(everything(), ~ ifelse(. == "Strength", 1, 0))) %>%
    mutate(across(everything(), ~ ifelse(is.na(.), 0, .))) %>%
    colSums() %>%
    order(decreasing = TRUE)
  
  # Get the column order using the names of the input data frame after indexing
  col_order <- names(sw)[index] 
  
  # Convert input data to a plain dataframe
  sw <- data.frame(sw)

  # Create a likert object
  likert_sw <- likert::likert(sw)

  # Plot the likert object using the col_order
  plot(likert_sw, group.order = col_order) +
    labs(title = title) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r, fig.width=6.5, dpi = 600}
data %>%
  select(sw_skills:sw_clinicianavail) %>%
  q9_plot(., "Overall")
```

```{r, fig.width=6.5, dpi = 600}
data %>%
  filter(Role == "Clinician/Provider") %>%
  select(sw_skills:sw_clinicianavail) %>%
  q9_plot(., "Clinician/Provider")
```

```{r, fig.width=6.5, dpi = 600}
data %>%
  filter(Role == "Staff") %>%
  select(sw_skills:sw_clinicianavail) %>%
  q9_plot(., "Staff")
```


# Q10: Among patients at your clinic, do you think that any of the following groups experience worse health than that of Colorado residents in general? (Select all that apply)
```{r}
df <- data %>%
    select(hi_race_q1___1:hi_race_q1____67) %>%
    mutate(across(everything(), ~ ifelse(!is.na(.), 1, 0)))

df_names <- names(df)

index <- df %>%
  colSums() %>%
  order(decreasing = TRUE)

ordered_names <- df_names[index]

df %<>%
  select(all_of(ordered_names)) %>%
  mutate(across(everything(), ~ factor(., levels = c("0", "1"))))

vars <- names(df)

# modify the column header labels for display
var_labs <- labels %>%
  select(all_of(vars)) %>%
  as.character() %>%
  str_remove(".*=") %>%           # removes all characters before '='
  gsub('.{1}$', '', .) %>%        # removes the 1st character from the end ')'
  str_replace("<br>", '') %>%     # removes the '<br>' if available
  str_trim()                      # removes any trailing white space


bind_cols(df, data.frame(Role = data$Role)) %>%
  tbl_summary(by = Role,
              value = list(vars[1] ~ "1",
                           vars[2] ~ "1",
                           vars[3] ~ "1",
                           vars[4] ~ "1",
                           vars[5] ~ "1",
                           vars[6] ~ "1",
                           vars[7] ~ "1",
                           vars[8] ~ "1",
                           vars[9] ~ "1",
                           vars[10] ~ "1",
                           vars[11] ~ "1",
                           vars[12] ~ "1"),
              label = list(vars[1] ~ var_labs[1],
                           vars[2] ~ var_labs[2],
                           vars[3] ~ var_labs[3],
                           vars[4] ~ var_labs[4],
                           vars[5] ~ var_labs[5],
                           vars[6] ~ var_labs[6],
                           vars[7] ~ var_labs[7],
                           vars[8] ~ var_labs[8],
                           vars[9] ~ var_labs[9],
                           vars[10] ~ var_labs[10],
                           vars[11] ~ var_labs[11],
                           vars[12] ~ var_labs[12])
              ) %>%
  add_overall() %>%
  modify_header(label = "") %>%
  as_gt()
```


<!-- If there are responses, then display them . -->
```{r}
n_responses <- data %>%
  select(hi_race_frsp1) %>%
  drop_na() %>%
  nrow()
```

`r if(n_responses != 0){'## Other race/ethnicity (please specify)'}`
```{r}
if(n_responses != 0) {
  show_table <- TRUE
} else {
  show_table <- FALSE
}
```

```{r, eval=show_table}
data %>%
  select(hi_race_frsp1) %>%
  drop_na() %>%
  gt::gt()
```

<!-- If there are responses, then display them . -->
```{r}
# Clean the cliff hanger response in frsp2
data <- data %>%
  mutate(hi_race_frsp2 = ifelse(
    hi_race_frsp2 == 'Personal/political beliefs about health are', 
    NA, 
    hi_race_frsp2))

n_responses <- data %>%
  select(hi_race_frsp2) %>%
  drop_na() %>%
  nrow()
```

`r if(n_responses != 0){'## Other'}`
```{r}
if(n_responses != 0) {
  show_table <- TRUE
} else {
  show_table <- FALSE
}
```

```{r, eval=show_table}
data %>%
    select(hi_race_frsp2) %>%
    drop_na() %>%
    gt::gt()
```


# Q11: Overall, how confident are you in your ability to provide the same quality of care to patients with disability as you provide to patients without disability.
```{r}
data %>%
  select(Role, confidence_disability) %>%
  freq_prop_tab()
```


# Q12: Please tell us how much each of the following is a barrier for you in caring for patients with disability...?
```{r}
data %>%
  select(Role, disability_time:disability_other) %>%
  freq_prop_tab()
```

<!-- If there are responses, then display them . -->
```{r}
n_responses <- data %>%
  select(barriers_frsp) %>%
  drop_na() %>%
  nrow()
```

`r if(n_responses != 0){'## Please specify if "Something else" is selected.'}`
```{r}
if(n_responses != 0) {
  show_table <- TRUE
} else {
  show_table <- FALSE
}
```

```{r, eval=show_table}
data %>%
  select(barriers_frsp) %>%
  drop_na() %>%
  gt::gt()
```


# Q13: Please rate how much you agree or disagree with the following statements:
```{r}
data %>%
  select(Role, org_awareness:org_collab) %>%
  freq_prop_tab()
```


# Q14: Are there people or organizations in the community, at UCH, or at the University of Colorado that could be partners to try to address health inequities among patients at your clinic?
```{r}
data %>%
  select(hi_partners_q1) %>%
  drop_na() %>%
  gt::gt()
```


